---
title: "2017to2022_trend_anal"
author: "Sonya Havens"
date: "2022-10-25"
output: html_document:
  keep.md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, include = FALSE}
library(tidyverse)
library(janitor)
library(here)
library(ggridges)
library(viridis)
library(viridisLite)
library(patchwork)
library(ggrepel)
library(lubridate)
```

```{r source_themes, include = FALSE}
source(here("functions", "theme_SH_pubs.R"))
```

This file merges all of the Sample Master datasets (post 2017) and then plots the julian date versus the result for each parameter at each site.

Load each annual Sample Master dataset, clean/rename the parameter and result column names, and filter for sample_number, collect_date, site, parameter, and result. 
```{r load_SM_data}

LTER_2017_orig <- read_csv(here("data", "2017_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2017 <- LTER_2017_orig %>% 
  select(sample_number, collect_date, site, parameter, result)


LTER_2018_orig <- read_csv(here("data", "2018_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2018 <- LTER_2018_orig %>% 
  select(sample_number, collect_date, site, parameter, result)


LTER_2019_orig <- read_csv(here("data", "2019_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2019 <- LTER_2019_orig %>% 
  select(sample_number, collect_date, site, parameter, result)


LTER_2020_orig <- read_csv(here("data", "2020_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2020 <- LTER_2020_orig %>% 
  select(sample_number, collect_date, site, parameter, result)


LTER_2021_orig <- read_csv(here("data", "2021_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2021 <- LTER_2021_orig %>% 
  select(sample_number, collect_date, site, parameter, result)


LTER_2022_orig <- read_csv(here("data", "2022_LTER_data.csv")) %>% 
  clean_names() %>% 
  rename(parameter = param) %>% 
  rename(result = numeric_result)

LTER_2022 <- LTER_2022_orig %>% 
  select(sample_number, collect_date, site, parameter, result)
```

Merge all of the annual Sample Master datasets
```{r merge_SM_datasets}

LTER_SM_merged <- bind_rows(lst(LTER_2017, LTER_2018, LTER_2019, LTER_2020, LTER_2021, LTER_2022), .id = "batch")

glimpse(LTER_SM_merged)

```

Clean the parameter names, and then filter for useful parameters
```{r clean_SM_param_names}

LTER_SM_wide <- LTER_SM_merged %>% 
  distinct() %>% 
  pivot_wider(names_from = parameter, values_from = result) %>% 
  clean_names() %>% 
  rename(nh3n = nh3_n) %>% 
  rename(no3n = no3_n) %>% 
  rename(no2n = no2_n) %>% 
  rename(partc = part_c) %>% 
  rename(partn = part_n) %>% 
  rename(partp = part_p) %>% 
  rename(partfe = part_fe) %>% 
  rename(ph = p_h) %>% 
  rename(srsi = sr_si)

glimpse(LTER_SM_wide)

LTER_SM_filtered <- LTER_SM_wide %>% 
  select(sample_number, collect_date, site, alk, cl, so4, ca, fe, k, mg, mn, na, chla, dic, doc, nh3n, no2n, no3n, partc, partn, partp, partfe, ph, srsi, tdn, tdp, cond, o2, a254, e2_e3, e2_e4, s275_295, s350_400, sr, suva, air_temperature, black_ice, integrated_epi_to_1_percent_surface_par, secchi_depth, snow_depth, thermal_epi_depth, thermocline_depth, white_ice_layer)

glimpse(LTER_SM_filtered)

```


Pivot back to long
```{r}

LTER_SM_long <- LTER_SM_filtered %>% 
  pivot_longer(cols = c(-sample_number, -collect_date, -site), names_to = "parameter", values_to = "result")

glimpse(LTER_SM_long)
```

Convert date from chr to date and add new columns for year and julian day, which are extracted from the date
```{r}
  
LTER_SM <- LTER_SM_long %>% 
  mutate(collect_date = mdy(collect_date)) %>% 
  mutate(year = year(collect_date)) %>% 
  mutate(julian = yday(collect_date))
 
glimpse(LTER_SM)
```

# Alkalinity 
```{r alk_plot}
alk <- LTER_SM %>% 
  filter(parameter == "alk") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Alkalinity") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_alk_trend_anal.pdf"), alk,
       width = 432, height = 558, units = "mm")
```

# Chloride
```{r cl_plot}
cl <- LTER_SM %>% 
  filter(parameter == "cl") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Chloride") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_cl_trend_anal.pdf"), cl,
       width = 432, height = 558, units = "mm")
```

# Sulfate
```{r so4_plot}
so4 <- LTER_SM %>% 
  filter(parameter == "so4") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Sulfate") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_so4_trend_anal.pdf"), so4,
       width = 432, height = 558, units = "mm")
```

# Iron
```{r fe_plot}
fe <- LTER_SM %>% 
  filter(parameter == "fe") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Iron") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_fe_trend_anal.pdf"), fe,
       width = 432, height = 558, units = "mm")
```

# Potassium
```{r k_plot}
k <- LTER_SM %>% 
  filter(parameter == "k") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Potassium") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_k_trend_anal.pdf"), k,
       width = 432, height = 558, units = "mm")
```

# Magnesium
```{r mg_plot}
mg <- LTER_SM %>% 
  filter(parameter == "mg") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Magnesium") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_mg_trend_anal.pdf"), mg,
       width = 432, height = 558, units = "mm")
```

# Manganese
```{r mn_plot}
mn <- LTER_SM %>% 
  filter(parameter == "mn") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Manganese") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_mn_trend_anal.pdf"), mn,
       width = 432, height = 558, units = "mm")
```

# Sodium
```{r na_plot}
na <- LTER_SM %>% 
  filter(parameter == "na") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Sodium") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_na_trend_anal.pdf"), na,
       width = 432, height = 558, units = "mm")
```

# Chlorophyll-a
```{r chla_plot}
chla <- LTER_SM %>% 
  filter(parameter == "chla") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Chlorophyll-a") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_chla_trend_anal.pdf"), chla,
       width = 432, height = 558, units = "mm")
```

# Conductivity
```{r cond_plot}
cond <- LTER_SM %>% 
  filter(parameter == "cond") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Conductivity") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_cond_trend_anal.pdf"), cond,
       width = 432, height = 558, units = "mm")
```

# Dissolved inorganic carbon
```{r dic_plot}
dic <- LTER_SM %>% 
  filter(parameter == "dic") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Dissolved inorganic carbon") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_dic_trend_anal.pdf"), dic,
       width = 432, height = 558, units = "mm")
```

# Dissolved organic carbon
```{r doc_plot}
doc <- LTER_SM %>% 
  filter(parameter == "doc") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Dissolved organic carbon") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_doc_trend_anal.pdf"), doc,
       width = 432, height = 558, units = "mm")
```

# Dissolved oxygen
```{r o2_plot}
o2 <- LTER_SM %>% 
  filter(parameter == "o2") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Dissolved oxygen") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_o2_trend_anal.pdf"), o2,
       width = 432, height = 558, units = "mm")
```

# Ammonia (as N)
```{r nh3n_plot}
nh3n <- LTER_SM %>% 
  filter(parameter == "nh3n") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Ammonia") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_nh3n_trend_anal.pdf"), nh3n,
       width = 432, height = 558, units = "mm")
```

# Nitrite (as N)
```{r no2n_plot}
no2n <- LTER_SM %>% 
  filter(parameter == "no2n") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Nitrite") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_no2n_trend_anal.pdf"), no2n,
       width = 432, height = 558, units = "mm")
```

# Nitrate (as N)
```{r no3n_plot}
no3n <- LTER_SM %>% 
  filter(parameter == "no3n") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Nitrate") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_no3n_trend_anal.pdf"), no3n,
       width = 432, height = 558, units = "mm")
```

# Particulate carbon
```{r partc_plot}
partc <- LTER_SM %>% 
  filter(parameter == "partc") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Particulate carbon") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_partc_trend_anal.pdf"), partc,
       width = 432, height = 558, units = "mm")
```

# Particulate nitrogen
```{r partn_plot}
partn <- LTER_SM %>% 
  filter(parameter == "partn") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Particulate nitrogen") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_partn_trend_anal.pdf"), partn,
       width = 432, height = 558, units = "mm")
```

# Particulate phosphorus
```{r partp_plot}
partp <- LTER_SM %>% 
  filter(parameter == "partp") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Particulate phosphorus") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_partp_trend_anal.pdf"), partp,
       width = 432, height = 558, units = "mm")
```

# Particulate iron
```{r partfe_plot}
partfe <- LTER_SM %>% 
  filter(parameter == "partfe") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Particulate iron") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_partfe_trend_anal.pdf"), partfe,
       width = 432, height = 558, units = "mm")
```

# pH
```{r ph_plot}
ph <- LTER_SM %>% 
  filter(parameter == "ph") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("pH") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_ph_trend_anal.pdf"), ph,
       width = 432, height = 558, units = "mm")
```

# Soluble reactive silicon
```{r srsi_plot}
srsi <- LTER_SM %>% 
  filter(parameter == "srsi") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Soluble reactive silicon") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_srsi_trend_anal.pdf"), srsi,
       width = 432, height = 558, units = "mm")
```

# Total dissolved nitrogen
```{r tdn_plot}
tdn <- LTER_SM %>% 
  filter(parameter == "tdn") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Total dissolved nitrogen") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_tdn_trend_anal.pdf"), tdn,
       width = 432, height = 558, units = "mm")
```

# Total dissolved phosphorus
```{r tdp_plot}
tdp <- LTER_SM %>% 
  filter(parameter == "tdp") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Total dissolved phosphorus") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_tdp_trend_anal.pdf"), tdp,
       width = 432, height = 558, units = "mm")
```

# Absorbace at 254 nm
```{r a254_plot}
a254 <- LTER_SM %>% 
  filter(parameter == "a254") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Absorbance at 254 nm") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_a254_trend_anal.pdf"), a254,
       width = 432, height = 558, units = "mm")
```

# e2:e3
```{r e2_e3_plot}
e2_e3 <- LTER_SM %>% 
  filter(parameter == "e2_e3") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("e2:e3") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_e2_e3_trend_anal.pdf"), e2_e3,
       width = 432, height = 558, units = "mm")
```

# e2:e4
```{r e2_e4_plot}
e2_e4 <- LTER_SM %>% 
  filter(parameter == "e2_e4") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("e2:e4") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_e2_e4_trend_anal.pdf"), e2_e4,
       width = 432, height = 558, units = "mm")
```

# Spectral slope between 275 and 295 nm
```{r s275_295_plot}
s275_295 <- LTER_SM %>% 
  filter(parameter == "s275_295") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Spectral slope between 275 and 295 nm") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_s275_295_trend_anal.pdf"), s275_295,
       width = 432, height = 558, units = "mm")
```

# Spectral slope between 350 and 400 nm
```{r s350_400_plot}
s350_400 <- LTER_SM %>% 
  filter(parameter == "s350_400") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Spectral slope between 275 and 295 nm") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_s350_400_trend_anal.pdf"), s350_400,
       width = 432, height = 558, units = "mm")
```

# Spectral slope ratio
```{r sr_plot}
sr <- LTER_SM %>% 
  filter(parameter == "sr") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Spectral slope ratio") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_sr_trend_anal.pdf"), sr,
       width = 432, height = 558, units = "mm")
```

# SUVA
```{r suva_plot}
suva <- LTER_SM %>% 
  filter(parameter == "suva") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("SUVA") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_suva_trend_anal.pdf"), suva,
       width = 432, height = 558, units = "mm")
```

# Air temperature
```{r air_temperature_plot}
air_temperature <- LTER_SM %>% 
  filter(parameter == "air_temperature") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Air temperature") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_air_temperature_trend_anal.pdf"), air_temperature,
       width = 432, height = 558, units = "mm")
```

# Black ice
```{r black_ice_plot}
black_ice <- LTER_SM %>% 
  filter(parameter == "black_ice") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Black ice") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_black_ice_trend_anal.pdf"), black_ice,
       width = 432, height = 558, units = "mm")
```

# Integrated epi to 1% surface par
```{r integrated_epi_to_1_percent_surface_par_plot}
integrated_epi_to_1_percent_surface_par <- LTER_SM %>% 
  filter(parameter == "integrated_epi_to_1_percent_surface_par") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Integrated epi to 1% surface par") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_integrated_epi_to_1_percent_surface_par_trend_anal.pdf"), integrated_epi_to_1_percent_surface_par,
       width = 432, height = 558, units = "mm")
```

# Secchi depth
```{r secchi_depth_plot}
secchi_depth <- LTER_SM %>% 
  filter(parameter == "secchi_depth") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Secchi depth") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_secchi_depth_trend_anal.pdf"), secchi_depth,
       width = 432, height = 558, units = "mm")
```

# Snow depth
```{r snow_depth_plot}
snow_depth <- LTER_SM %>% 
  filter(parameter == "snow_depth") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Snow depth") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_snow_depth_trend_anal.pdf"), snow_depth,
       width = 432, height = 558, units = "mm")
```

# Thermal epi depth
```{r thermal_epi_depth_plot}
thermal_epi_depth <- LTER_SM %>% 
  filter(parameter == "thermal_epi_depth") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Thermal epi depth") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_thermal_epi_depth_trend_anal.pdf"), thermal_epi_depth,
       width = 432, height = 558, units = "mm")
```

# Thermocline depth
```{r thermocline_depth_plot}
thermocline_depth <- LTER_SM %>% 
  filter(parameter == "thermocline_depth") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("Thermocline depth") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_thermocline_depth_trend_anal.pdf"), thermocline_depth,
       width = 432, height = 558, units = "mm")
```

# White ice layer
```{r white_ice_layer_plot}
white_ice_layer <- LTER_SM %>% 
  filter(parameter == "white_ice_layer") %>% 
   drop_na() %>% 

  ggplot() +
  facet_wrap(~ site) +
  geom_point(aes(x = julian, y = result, colour = year)) +
  geom_path(aes(x = julian, y = result, colour = year)) +
  ggtitle("White ice layer") +
  theme_SH_pubs() +
  scale_color_viridis()
  
ggsave(here("figures", "2017to2022_white_ice_layer_trend_anal.pdf"), white_ice_layer,
       width = 432, height = 558, units = "mm")
```


```{r timestamp}
str_c("This report was created on", Sys.Date(), sep = " ")
```
